---
title: "Statistical Inference Assigment, Part A"
author: "Fabio Fornari"
date: "December 26, 2015"
output: word_document
---

In this simulation, it will be investigated the distribution of averages of 40 exponentials. To do that we need to do a thousand simulated averages of 40 exponentials. The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also also 1/lambda. Lambda is set to 0.2 for all of the simulations.
The code to do this is as follows.

```{r}
set.seed(109)
nSim = 1000
n <- 40
lambda <- 0.2
simulations <- data.frame(x=replicate(nSim, mean(rexp(n, lambda))))
```


### Questions 1
Show the sample mean and compare it to the theoretical mean of the distribution.

```{r}
simulated_mean <- mean(simulations$x)
simulated_mean
```

The mean of the means of 1000 simulations of 40 exponential is `r sprintf("%.4f", simulated_mean)`, which is very close to the expected mean (population mean) of 1/lambda = 5.0.


### Questions 2
Show how variable the sample is (via variance) and compare it to the theoretical variance of the distribution.

```{r}
simulated_sd <- sd(simulations$x)
simulated_sd
```
```{r}
expected_sd <- (1/lambda)/sqrt(n)
expected_sd
```
```{r}
simulated_variance <- var(simulations$x)
simulated_variance
```
```{r}
expected_variance <- ((1/lambda)/sqrt(n))^2
expected_variance
```
The simulated standard deviation is `r sprintf("%.4f", simulated_sd)`, close to the expected standard deviation of `r sprintf("%.4f", expected_sd)`
The simulated variance of the distributions population is `r sprintf("%.3f", simulated_variance)` close to the expetected variance of `r sprintf("%.3f", expected_variance)`.


### Question 3
Show that the distribution is approximately normal.

Below is a histogram plot of 1000 simulations of exponentials rexp(nSim, lambda). As can be seen this simulations is not normally distributed.

```{r}
library(ggplot2)
set.seed(109)
simulations_2 <- data.frame(x=rexp(nSim, lambda))
g2 <- ggplot(data = simulations_2, aes(x = x)) + 
      geom_histogram(aes(y=..density..), fill = 'lightblue', 
                    binwidth = 0.5, color = 'black') 
print(g2)
```

Below is a histogram plot of the means of the 1000 simulations of rexp(n, lambda). It is overlaid with a normal distribution with mean 5 and standard deviation 0.7906. As can be seen the simulations appears to be approximately normally distributed.

```{r}
g <- ggplot(data = simulations, aes(x = x)) + 
     geom_histogram(aes(y=..density..), fill = 'lightblue', 
                    binwidth = 0.3, color = 'black') 
g <- g + stat_function(fun = dnorm, arg = list(mean = 5, sd =   
     expected_sd), size = 2, aes(colour = 'darkblue'))
g <- g + scale_colour_manual(name='Legend', values=c('darkblue'), labels='Normal Distribution')
g <- g + theme(legend.position="bottom")
print(g)
```